---
title: "Contact Experiment Data Analysis"
output: html_notebook
---
#!diagnostics suppress=<Extreme1, Extreme2>
First Step is to load the necessary package, If you dont have them just install them. For jjstatsplot you need to install it remotely.
Just remove the dash and press enter. Then Press 3 (none package to be updated). 
?group_by()

```{r}
#remotes::install_github("sbalci/jjstatsplot") #Press 3 !!!!! i.e., installing/Updating none package! 
library(jmv)
library(datasets)
library(plyr)
library(readr)
library(dataframes2xls)
library(data.table)
library(plyr)
library(ggstatsplot)
library(jjstatsplot)
library(lme4)
library(lmerTest)
library(ggplot2)
library(rstatix)
library(coin)
library(ARTool)
library(ggpubr)
library(tidyverse)
library(dplyr)

#!diagnostics suppress=<Extreme1, Extreme2>
```



Import and merge all the csv files (x.csv where x = ID) of the folder. Note, that the ID is has already been added as column 
```{r}
data <- list.files(path = "C:/Users/pkourtes/Desktop/ContactExperiment/Results/Participants/MergingFolder",     # Identify all csv files in folder
                       pattern = "*.csv", full.names = TRUE) %>% 
  lapply(read_csv) %>%                                            # Store all files in list
  bind_rows                                                       # Combine data sets into one data set 
data 
```


Discard first X trials per interpenetration feedback condition and then create a summary
table for each participant. You need to define **nrTrialsPerBlockToRemove**.
```{r}

nrTrialsPerBlockToRemove <- 1
#trialsToRemove <- seq(from = 1, to = nrTrialsPerBlockToRemove)

  data <-  data %>%
    group_by(ID, Block, InterpenetrationFeedback, FullyShaded) %>% # I have added here the fully shaded 
    slice(nrTrialsPerBlockToRemove+1:n())
  # to double check we are discarding the right rows
  #print(data[[i]]$Trial)

 # This df will be used to create the subsets for 1st part and 2nd part of the experiment. 

  is.factor(data$InterpenetrationFeedback)
  is.factor(data$FullyShaded)
  is.numeric(data$InterpenetrationFeedback)
  
data$InterpenetrationFeedback  <- as.factor(data$InterpenetrationFeedback)
data$FullyShaded <- as.factor(data$FullyShaded)
```
  
#!diagnostics suppress=<Extreme1, Extreme2>
Discard unnecessary variables 
```{r}
NewData <- data
#NewData <- select(NewData, -c("Trial", "TrialInBlock", "NrOfAdjustments" , "Completed" , "Attempts" , "Skipped"))
names(NewData)
```

Let's average the data. This will create 8 (Eight) averaged rows per participant. 
The logic is 4 Types of interpenetration feedback * 2 Shade conditions (4 x 2 = 8)   
```{r}  
Averaged_Data <- aggregate(. ~ ID + Age + Gender + InterpenetrationFeedback + FullyShaded, NewData, mean)


df <- Averaged_Data # A more Convenient name for our dataset

```

#!diagnostics suppress=<Extreme1, Extreme2>
Convert from meters to cm  
```{r}
df$MaxInterpenetration <- df$MaxInterpenetration * 100
df$AverageInterpenetration <- df$AverageInterpenetration * 100
df$AverageOffsetFromSurface <- df$AverageOffsetFromSurface * 100

```


Check the distribution of the main dependent variables using histograms
```{r}
hist(df$MaxInterpenetration)
hist(df$AverageInterpenetration)
```
Based on the histograms, the distribution is heavily positively skewed, which is not good, probably we ve violated the normality assumption
Let's check the normality assumption (i.e., whether we have normal distribution or not)
```{r}
shapiro_test(df$MaxInterpenetration)
shapiro_test(df$AverageInterpenetration)
ggqqplot(df$MaxInterpenetration)
ggqqplot(df$AverageInterpenetration)

#Let's check the assumption for each interpenetration feedback and shade condition
df %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(MaxInterpenetration) #It is violated!

df %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(AverageInterpenetration)  #It is violated!

```

#!diagnostics suppress=<Extreme1, Extreme2>
OK, we have significant results which means that we have violated the normality assumption (i.e, abnormal distribution).
Let's try to identify the outliers
```{r}
# One df for outliers (1.5 coeff), one for extremes (3 coeff)
df2 <- df
###############################


df_outliers <- identify_outliers(df, variable = "MaxInterpenetration") #we have several ones
df_outliers2  <- identify_outliers(df, variable = "MaxInterpenetration")


df$Outlier <- is_outlier(df$MaxInterpenetration) #Let's make another variable indicating whether the row is an outlier or not
df$Outlier2 <- is_outlier(df$AverageInterpenetration)

df$Extreme1 <- is_extreme(df$MaxInterpenetration)

df$Extreme2 <- is_extreme(df$AverageInterpenetration)


####### Only extreme values for df2

df_Extremes <- identify_outliers(df, variable = "MaxInterpenetration", coef = 3) #we have several ones
df_Extremes2  <- identify_outliers(df, variable = "MaxInterpenetration", coef = 3)

df2$Extreme1 <- is_extreme(df2$MaxInterpenetration)

df2$Extreme2 <- is_extreme(df2$AverageInterpenetration)

```
#!diagnostics suppress=<Extreme1, Extreme2>
Let's try to solve it by omitting the outliers 
```{r}
df$Outlier[df$Outlier == TRUE]  <- NA
df$Outlier2[df$Outlier2 == TRUE]  <- NA

df_clean <- na.omit(df) #We omit the rows which have NA values !!! and we create a new dataset without outliers.

#we check again the histograms, qqplots, and normality assumption
hist(df_clean$MaxInterpenetration) 
hist(df_clean$AverageInterpenetration) #better than before but stil skewed
shapiro_test(df_clean$MaxInterpenetration)
shapiro_test(df_clean$AverageInterpenetration) # violated!
ggqqplot(df_clean$MaxInterpenetration)
ggqqplot(df_clean$AverageInterpenetration) #qqplots are good.

df_clean %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(MaxInterpenetration) #Still some violate the assumption

df_clean %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(AverageInterpenetration) #Still some violate the assumption
 


################# Let's do the same just only for the extreme values

df2$Extreme1[df2$Extreme1 == TRUE]  <- NA
df2$Extreme2[df2$Extreme2 == TRUE]  <- NA

df2_clean <- na.omit(df2) #We omit the rows which have NA values !!! and we create a new dataset without outliers.


df2_clean %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(MaxInterpenetration) #Still some violate the assumption



df2_clean %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(AverageInterpenetration) #Still some violate the assumption
 
```

OK the distribution is better now but again it violates the normality assumption

Let's try to correct the problem with the Normality of the Variance. 
The reason, as we can see above by checking the histograms, is that the distribution is very positively skewed.
We dont want any type of an intense skew (Though, always there is somewhat of skewness in the data). 
```{r}
#A common thing to resolve the positive skewness is to covert the IVs into logarithms 

df_clean$MaxInterpenetration <- log10(df_clean$MaxInterpenetration)

df_clean$AverageInterpenetration <- log10(df_clean$AverageInterpenetration)

#we check again the histograms, qqplots, and normality assumption
hist(df_clean$MaxInterpenetration) 
hist(df_clean$AverageInterpenetration) # WoW, they seems like normally distributed
shapiro_test(df_clean$MaxInterpenetration) #WOW! That's it Normal Distribution
shapiro_test(df_clean$AverageInterpenetration) # YEAH! Normal Distribution ladies and gentlemen :) 
ggqqplot(df_clean$MaxInterpenetration)
ggqqplot(df_clean$AverageInterpenetration) #qqplots are still good.


df_clean %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(MaxInterpenetration)

df_clean %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(AverageInterpenetration)
# No Violations . We are ready for Two Way Repeated Measures ANOVA



####################### The same for the df where we excluded only the extreme values (i.e., coeff = or > 3)

df2_clean$MaxInterpenetration <- log10(df2_clean$MaxInterpenetration)

df2_clean$AverageInterpenetration <- log10(df2_clean$AverageInterpenetration)

#we check again the histograms, qqplots, and normality assumption
hist(df2_clean$MaxInterpenetration) 
hist(df2_clean$AverageInterpenetration) # WoW, they seems like normally distributed
shapiro_test(df2_clean$MaxInterpenetration) #WOW! That's it Normal Distribution
shapiro_test(df2_clean$AverageInterpenetration) # YEAH! Normal Distribution ladies and gentlemen :) 
ggqqplot(df2_clean$MaxInterpenetration)
ggqqplot(df2_clean$AverageInterpenetration) #qqplots are still good.


df2_clean %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(MaxInterpenetration)

df2_clean %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(AverageInterpenetration)
# No Violations . We are ready for Two Way Repeated Measures ANOVA


# However 
#It seems that many of the outliers (> 1.5 coeff) were also extremes (> 3 coeff) 
# While all the outliers and the extremes derive from the IDs : 9 , 17 , and 20

```

#!diagnostics suppress=<Extreme1, Extreme2>
Another Solution for solving the normality violation
```{r}
#Another more extreme solution for positive skewness
# For extreme cases, we can also try also to divide 1 by our values (Re assign )

# df_clean$MaxInterpenetration <- 1/df_clean$MaxInterpenetration

# df_clean$AverageInterpenetration <- 1/df_clean$AverageInterpenetration

```



let's check the plots of the means to see what happens in our cleaned data.

```{r}
# We are going to prefer the one where we excluded only the extreme values
# so df2_clean will be the df that we will use

# The first two blocks comparing IVs effect on DV
p1 <- ggstatsplot::ggbetweenstats(
  data = df2_clean,
  x = "InterpenetrationFeedback", #Indepedent Variable
  y = "MaxInterpenetration", # Depedent Variable
  grouping.var = "FullyShaded", # 2nd IV 
  type = "p", # parametric test i.e., p values
  pairwise.comparisons = TRUE, #compute pairwise comparisons
  pairwise.display = "significant", 
  p.adjust.method = "bonferroni", # correction of p-value
  effsize.type = "unbiased", # Calculates the Hedge's g for t tests and the partial Omega for ANOVA
  xlab = "Type of Feedback", #label of X axis
  ylab = "Maximum Interpenetration", #label of y axis
  var.equal = TRUE, #Assuming Equal variances
  mean.ci = TRUE, #display the confidence interval of the mean
  notch = TRUE, #Compare the medians i.e., IQR with 95% confidence interval
  paired = TRUE #indicating that we have a within subject design
  ) 

p2 <- ggstatsplot::ggbetweenstats(
  data = df2_clean,
  x = "InterpenetrationFeedback",
  y = "AverageInterpenetration",
  grouping.var = "FullyShaded",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
)


# Replicating the above but this time we look on the effect of the type of feedback on the DVs when the shaded is true and when it is false.
p3 <- ggstatsplot::grouped_ggbetweenstats(
  data = df2_clean,
  x = "InterpenetrationFeedback",
  y = "MaxInterpenetration",
  grouping.var = "FullyShaded",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p4 <- ggstatsplot::grouped_ggbetweenstats(
  data = df2_clean,
  x = "InterpenetrationFeedback",
  y = "AverageInterpenetration",
  grouping.var = "FullyShaded",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 

# Lets check the effect of shaded condition on DVs
p5 <- ggstatsplot:: ggbetweenstats(
  data = df2_clean,
  x = "FullyShaded",
  y = "MaxInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p6 <- ggstatsplot::ggbetweenstats(
  data = df2_clean,
  x = "FullyShaded",
  y = "AverageInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 

p7 <- ggstatsplot::grouped_ggbetweenstats(
  data = df2_clean,
  x = "FullyShaded",
  y = "MaxInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p8 <- ggstatsplot::grouped_ggbetweenstats(
  data = df2_clean,
  x = "FullyShaded",
  y = "AverageInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 
p1

p2

p3 

p4

p5 

p6

p7

p8

plist <- list(p1,p2)
plist2 <- list(p3,p4)
plist3 <- list(p5,p6)
plist4 <- list(p7,p8)

combine_plots(
  plotlist = plist, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist2, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist3, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist4, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

```
So based on the above plots we can see that
###############################################
For the maximum interpenetration (plot 1): 

the both, electrotactile, and visual types of feedback are significantly better than no feedback. 
while there NOT significant differences amongst them. 
Another important info is the effect size based on partial omega squared which is 0.20 i.e., the effect size is large

Reference for interpreting Omega Squared
Small effect: ω2 = 0.01;
Medium effect: ω2 = 0.06;
Large effect: ω2 = 0.14.

Also, the logarith of Bayes Factor [ Log(BF01) ] for testing hypotheses is -14.86 
which means that there are extremely strong evidence in favor of H1 alternative hypothesis. 


##############
For averaged interpenentration (plot2):

Similar to the results for the maximum interpenetration


#############################################################################################################
For the relationship between the shade condition and the type of feedback on 

##########
maximum interpenetration (plot3) & averaged interpenetration (plot4):

We can see that the results are similar to the plot1 when the shaded condition is false (i.e., when there is not an explicit visual representation of the target object).

However, when the visual representation of the object is explicit (i.e., shaded = TRUE) then the effect of electrotactile feedback is substantially alleviated, 
which results to a non-significant difference between electrotactile and no-feedback conditions. In contrast, the visual and both conditions are still significantly different from the no-feedback condition. However, we can see that the range of the confidence intervals of the both condition is being stretched when the target is fully shaded (an explicit visual representation). 
In contrast, the range of the confidence intervals of visual condition remains intact or slightly decreases when the target's visual representation is explicit. 

Hence, we can theorize that an implicit visual representation of the target (i.e., non-fully shaded) increases the importance of the electrotactile feedback on the performance aspects. This also postulates that when the visual information is insufficient or ambiguous, then the electrotactile feedback complements the sensory information which facilitates visuospatial perception.


####################################
For the shaded condition alone, we can see that it doesn't have an effect on performance (plot 5 & 6) regardless of the type of feedback (plot 7 & 8) 



########################## To Move on ###################################
So, we saw that there is indeed an effect of IV levels (i.e., type of the interpenetration feedback) on the DVs, 
as well as that there is an interrelationship between the levels of the interpenetration feedback and the levels of the shaded condition., especially regarding electrotactile feedback.   

Let's check the Two Way Repeated Measures ANOVA now
#!diagnostics suppress=<Extreme1, Extreme2>
```{r}

RM2W_Max <- anova_test(
  data = df2_clean, dv = MaxInterpenetration, wid = ID,
  formula = MaxInterpenetration ~ InterpenetrationFeedback + FullyShaded + InterpenetrationFeedback*FullyShaded + (1|ID),
  within = c(InterpenetrationFeedback, FullyShaded)
  )
 get_anova_table(RM2W_Max)
 
RM2W_Av <- anova_test(
  data = df2_clean, dv = AverageInterpenetration, wid = ID,
  formula = AverageInterpenetration ~ InterpenetrationFeedback + FullyShaded + InterpenetrationFeedback*FullyShaded + (1|ID),
  )
 get_anova_table(RM2W_Av)
 
```
 
 There is neither a significant effect of the fully shaded on the DV, nor a significant interrelationship effect between fully shaded and interpenetration feedback. On the other hand Interpenetration feedback has a sign effect on DVs.
 
 
 So, lets go for an ONE Way Repeated Measures ANOVA now
```{r}

RM1W_Max <- anova_test(
  data = df2_clean, dv = MaxInterpenetration, wid = ID,
  formula = MaxInterpenetration ~ InterpenetrationFeedback + (1|ID),
  )
 get_anova_table(RM1W_Max )

RM1W_Av <- anova_test(
  data = df2_clean, dv = AverageInterpenetration, wid = ID,
  formula = AverageInterpenetration ~ InterpenetrationFeedback + (1|ID),
  )
 get_anova_table(RM1W_Av)
 

```

OK, there is significant effect of the interpenetration feedback on both DVs

#!diagnostics suppress=<Extreme1, Extreme2>
Let's go for the post hoc tests
```{r}

pwMax <- pairwise.t.test(df2_clean$MaxInterpenetration, df2_clean$InterpenetrationFeedback, p.adjust.method = "bonferroni",
        paired = FALSE, alternative = "two.sided")


pwAv <- pairwise.t.test(df2_clean$AverageInterpenetration, df2_clean$InterpenetrationFeedback, p.adjust.method = "bonferroni",
        paired = FALSE, alternative = "two.sided")


#require(effectsize)
#?hedges_g()

#effectsize::hedges_g("AverageInterpenetration", "InterpenetrationFeedback", data = df2_clean, correction = TRUE, paired = TRUE)


pwMax

pwAv
```

We have significant results but the paired = TRUE option wasn't possible because the levels of the IV do NOT have the same length (unbalanced data)

```{r}

```


 
 
 
 
 
 

 
 
If you run the ANOVA above then you will see that we get some errors indicating that don not have balanced data (i.e., unbalanced data)
 
 CORRECTION!!!!! 
 ################################  THE PROBLEM WAS IRRELEVANT TO THE DATA #################################################
 IT WAS a R Studio Bug. Though, the data are indeed unbalanced!!!!
 
 
 
 ######################## So we may go or not for the below ########################
 
 
 Possible solutions for unbalanced data: 
 
 1) Using the ezMixed function from the ez package, which wraps lmer and produces likelihood ratios (a superior metric of evidence)
 
 2) Deleting the IDs which produced the extreme values. However, we will reduce the sample size to N = 21.
 Also, the observations will be 21 (the participants) * 8 Conditions (i.e., 4 types of feedback * 2 Shaded conditions) = 168 observations
 
 3) To try and catch the extreme values before averaging the data! By doing that, we may be able to keep the N = 24. 
 Thanks Ferran :)
 
 
#!diagnostics suppress=<Extreme1, Extreme2> 
So, we will start from solution 3, because it is the best case scenario
```{r}

data$Extreme1 <- is_extreme(data$MaxInterpenetration)

data$Extreme2 <- is_extreme(data$AverageInterpenetration)

data$Extreme1[data$Extreme1 == TRUE]  <- NA
data$Extreme2[data$Extreme2 == TRUE]  <- NA

data_clean <- na.omit(data)

newDF <- data_clean
#newDF <- select(data_clean, -"Trial", -"TrialInBlock", -"NrOfAdjustments" ,
#                 -"Completed" , -"Attempts" , -"Skipped", -"Extreme1", -"Extreme2")

AVnewDF <- aggregate(. ~ ID + Age + Gender + InterpenetrationFeedback + FullyShaded, newDF, mean)

AVnewDF$MaxInterpenetration <- AVnewDF$MaxInterpenetration * 100
AVnewDF$MaxInterpenetration <- AVnewDF$MaxInterpenetration * 100
AVnewDF$MaxInterpenetration <- AVnewDF$MaxInterpenetration * 100

hist(AVnewDF$MaxInterpenetration) 
hist(AVnewDF$AverageInterpenetration) 
ggqqplot(AVnewDF$MaxInterpenetration)
ggqqplot(AVnewDF$AverageInterpenetration)
shapiro_test(AVnewDF$MaxInterpenetration)
shapiro_test(AVnewDF$AverageInterpenetration) 

AVnewDF %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(MaxInterpenetration)

AVnewDF %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(AverageInterpenetration)

# We still have a problem with distribution


#Try by converting the DVs into logarithms again 
AVnewDF$MaxInterpenetration <- log10(AVnewDF$MaxInterpenetration)

AVnewDF$AverageInterpenetration <- log10(AVnewDF$AverageInterpenetration)


hist(AVnewDF$MaxInterpenetration) 
hist(AVnewDF$AverageInterpenetration) 
ggqqplot(AVnewDF$MaxInterpenetration)
ggqqplot(AVnewDF$AverageInterpenetration)
shapiro_test(AVnewDF$MaxInterpenetration)
shapiro_test(AVnewDF$AverageInterpenetration) 

AVnewDF %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(MaxInterpenetration)

AVnewDF %>%
  group_by(InterpenetrationFeedback, FullyShaded) %>%
  shapiro_test(AverageInterpenetration)
############### PERFECT WE ARE GOOD TO GO !!!!!!!!!!!!!!!!!!!!!
```



Lets do the box-violin plots again
```{r}

p1 <- ggstatsplot::ggbetweenstats(
  data = AVnewDF,
  x = "InterpenetrationFeedback", #Indepedent Variable
  y = "MaxInterpenetration", # Depedent Variable
  grouping.var = "FullyShaded", # 2nd IV 
  type = "p", # parametric test i.e., p values
  pairwise.comparisons = TRUE, #compute pairwise comparisons
  pairwise.display = "significant", 
  p.adjust.method = "bonferroni", # correction of p-value
  effsize.type = "unbiased", # Calculates the Hedge's g for t tests and the partial Omega for ANOVA
  xlab = "Type of Feedback", #label of X axis
  ylab = "Maximum Interpenetration", #label of y axis
  var.equal = TRUE, #Assuming Equal variances
  mean.ci = TRUE, #display the confidence interval of the mean
  notch = TRUE, #Compare the medians i.e., IQR with 95% confidence interval
  paired = TRUE #indicating that we have a within subject design
  ) 

p2 <- ggstatsplot::ggbetweenstats(
  data = AVnewDF,
  x = "InterpenetrationFeedback",
  y = "AverageInterpenetration",
  grouping.var = "FullyShaded",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
)


# Replicating the above but this time we look on the effect of the type of feedback on the DVs when the shaded is true and when it is false.
p3 <- ggstatsplot::grouped_ggbetweenstats(
  data = AVnewDF,
  x = "InterpenetrationFeedback",
  y = "MaxInterpenetration",
  grouping.var = "FullyShaded",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p4 <- ggstatsplot::grouped_ggbetweenstats(
  data = AVnewDF,
  x = "InterpenetrationFeedback",
  y = "AverageInterpenetration",
  grouping.var = "FullyShaded",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 

# Lets check the effect of shaded condition on DVs
p5 <- ggstatsplot:: ggbetweenstats(
  data = AVnewDF,
  x = "FullyShaded",
  y = "MaxInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p6 <- ggstatsplot::ggbetweenstats(
  data = AVnewDF,
  x = "FullyShaded",
  y = "AverageInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 

p7 <- ggstatsplot::grouped_ggbetweenstats(
  data = AVnewDF,
  x = "FullyShaded",
  y = "MaxInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p8 <- ggstatsplot::grouped_ggbetweenstats(
  data = AVnewDF,
  x = "FullyShaded",
  y = "AverageInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 
p1

p2

p3 

p4

p5 

p6

p7

p8

plist <- list(p1,p2)
plist2 <- list(p3,p4)
plist3 <- list(p5,p6)
plist4 <- list(p7,p8)

combine_plots(
  plotlist = plist, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist2, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist3, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist4, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

```

The bad news are that now we do not have an effect between electrotactile and No Feedback conditions

Also, there is a significant difference between Both and Electrotactile Feedback. 

The rest remain as we interpreted above for the plots using the df_clean2 

#!diagnostics suppress=<Extreme1, Extreme2>
Let's check the Two Way Repeated Measures ANOVA now
```{r}

TwoWayAnovaRM_Max <- anova_test(
  data = AVnewDF, dv = MaxInterpenetration, wid = ID,
  formula = MaxInterpenetration ~  InterpenetrationFeedback*FullyShaded + (1|ID),
  within = c(InterpenetrationFeedback, FullyShaded)
  )

get_anova_table(TwoWayAnovaRM_Max )


TwoWayAnovaRM_Av <- anova_test(
  data = AVnewDF, dv = AverageInterpenetration, wid = ID,
  formula = AverageInterpenetration ~  InterpenetrationFeedback*FullyShaded + (1|ID),
  within = c(InterpenetrationFeedback, FullyShaded)
  )

get_anova_table(TwoWayAnovaRM_Av)

```

So, again there is no effect of the Fully Shade neither on DVs nor an interrelationship with Int feedback

So we go for OneWay Repeated Measures ANOVA
```{r}

OneWayAnovaRM_Max <- anova_test(
  data = AVnewDF, dv = MaxInterpenetration, wid = ID,
  formula = MaxInterpenetration ~  InterpenetrationFeedback + (1|ID)
  )

get_anova_table(OneWayAnovaRM_Max )


OneWayAnovaRM_Av <- anova_test(
  data = AVnewDF, dv = AverageInterpenetration, wid = ID,
  formula = AverageInterpenetration ~  InterpenetrationFeedback + (1|ID)
  )

get_anova_table(OneWayAnovaRM_Av)

```

So, we have significant effect of the IV on the DV 

So, we may now go for post hoc tests
```{r, echo=FALSE}

Max <- pairwise.t.test(AVnewDF$MaxInterpenetration, AVnewDF$InterpenetrationFeedback, p.adjust.method = "bonferroni",
        paired = FALSE, alternative = "two.sided")


Av <- pairwise.t.test(AVnewDF$AverageInterpenetration, AVnewDF$InterpenetrationFeedback, p.adjust.method = "bonferroni",
        paired = FALSE, alternative = "two.sided")




Max


Av

```

Again we have significant results but it didnt allow to me to used paired = TRUE. We get the same message as above that the length of the arguments do NOT have the same length. 









#######################################################################################################################
Let's check the difference between 1st and 2nd part

```{r}
# needed for ANOVA functions.
library("afex")     
  
newDF$Part <- as.factor(newDF$Block < 4)

levels(newDF$Part)

newDF$Part <- factor(newDF$Part,levels = c("TRUE","FALSE"),
                  labels = c("Part 1","Part 2"))


newDF_Parts <- aggregate(. ~ ID + Age + Gender + InterpenetrationFeedback + Part, newDF, mean)


```


```{r Anova, echo=FALSE}
?aov_ez()
a1 <- aov_ez("ID", "MaxInterpenetration", newDF_Parts,
             within = c("Part", "InterpenetrationFeedback"),
             anova_table = list(es = "pes"))

knitr::kable(nice(a1$anova_table))
```


```{r Anova, echo=FALSE}

a2 <- aov_ez("ID", "AverageInterpenetration", newDF_Parts,
             within = c("Part", "InterpenetrationFeedback"),
             anova_table = list(es = "pes"))

knitr::kable(nice(a2$anova_table))

```



```{r}

effectsize::omega_squared(a1, partial = TRUE, ci = 0.95)

```
Reference for interpreting Omega Squared
Small effect: ω2 = 0.01;
Medium effect: ω2 = 0.06;
Large effect: ω2 = 0.14.

```{r}

effectsize::omega_squared(a2, partial = TRUE, ci = 0.95)

```
Reference for interpreting Omega Squared
Small effect: ω2 = 0.01;
Medium effect: ω2 = 0.06;
Large effect: ω2 = 0.14.
```{r}

pw1 <- pairwise.t.test(newDF_Parts$AverageInterpenetration, newDF_Parts$InterpenetrationFeedback, p.adjust.method = "bonferroni",
        paired = FALSE, alternative = "two.sided")

pw1


effectsize::hedges_g("AverageInterpenetration", "Part", data = newDF_Parts, correction = TRUE, paired = TRUE)


is.factor(newDF_Parts$InterpenetrationFeedback)
levels(newDF_Parts$InterpenetrationFeedback)
```

```{r}

p1 <- ggstatsplot::ggbetweenstats(
  data = newDF_Parts,
  x = "InterpenetrationFeedback", #Indepedent Variable
  y = "MaxInterpenetration", # Depedent Variable
  grouping.var = "Part", # 2nd IV 
  type = "p", # parametric test i.e., p values
  pairwise.comparisons = TRUE, #compute pairwise comparisons
  pairwise.display = "significant", 
  p.adjust.method = "bonferroni", # correction of p-value
  effsize.type = "unbiased", # Calculates the Hedge's g for t tests and the partial Omega for ANOVA
  xlab = "Type of Feedback", #label of X axis
  ylab = "Maximum Interpenetration", #label of y axis
  var.equal = TRUE, #Assuming Equal variances
  mean.ci = TRUE, #display the confidence interval of the mean
  notch = TRUE, #Compare the medians i.e., IQR with 95% confidence interval
  paired = TRUE #indicating that we have a within subject design
  ) 

p2 <- ggstatsplot::ggbetweenstats(
  data = newDF_Parts,
  x = "InterpenetrationFeedback",
  y = "AverageInterpenetration",
  grouping.var = "Part",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
)


# Replicating the above but this time we look on the effect of the type of feedback on the DVs when the shaded is true and when it is false.
p3 <- ggstatsplot::grouped_ggbetweenstats(
  data = newDF_Parts,
  x = "InterpenetrationFeedback",
  y = "MaxInterpenetration",
  grouping.var = "Part",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p4 <- ggstatsplot::grouped_ggbetweenstats(
  data = newDF_Parts,
  x = "InterpenetrationFeedback",
  y = "AverageInterpenetration",
  grouping.var = "Part",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 

# Lets check the effect of shaded condition on DVs
p5 <- ggstatsplot:: ggbetweenstats(
  data = newDF_Parts,
  x = "Part",
  y = "MaxInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p6 <- ggstatsplot::ggbetweenstats(
  data = newDF_Parts,
  x = "Part",
  y = "AverageInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 

p7 <- ggstatsplot::grouped_ggbetweenstats(
  data = newDF_Parts,
  x = "Part",
  y = "MaxInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p8 <- ggstatsplot::grouped_ggbetweenstats(
  data = newDF_Parts,
  x = "Part",
  y = "AverageInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 
p1

p2

p3 

p4

p5 

p6

p7

p8

plist <- list(p1,p2)
plist2 <- list(p3,p4)
plist3 <- list(p5,p6)
plist4 <- list(p7,p8)

combine_plots(
  plotlist = plist, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist2, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist3, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist4, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")


```







###################################### Parsimonious Approach;: Without the IDs which produced Extreme Values #####################################

Now lets do all again but this time without the IDs which produced the Extreme Values
```{r}

ParsiDF <- NewData

ParsiDF$ID[ParsiDF$ID == 9] <- NA
ParsiDF$ID[ParsiDF$ID == 17] <- NA
ParsiDF$ID[ParsiDF$ID == 20] <- NA

ParsiDF <- na.omit(ParsiDF)

ParsiDF$Part <- as.factor(ParsiDF$Block < 4)

levels(ParsiDF$Part)

ParsiDF$Part <- factor(ParsiDF$Part,levels = c("TRUE","FALSE"),
                  labels = c("Part 1","Part 2"))

ParsiDF <- aggregate(. ~ ID + Age + Gender + InterpenetrationFeedback + Part, ParsiDF, mean)

shapiro_test(ParsiDF$MaxInterpenetration)
shapiro_test(ParsiDF$AverageInterpenetration)
ggqqplot(ParsiDF$MaxInterpenetration)
ggqqplot(ParsiDF$AverageInterpenetration)


ParsiDF %>%
  group_by(InterpenetrationFeedback, Part) %>%
  shapiro_test(MaxInterpenetration) 

ParsiDF %>%
  group_by(InterpenetrationFeedback, Part) %>%
  shapiro_test(AverageInterpenetration)  

ParsiDF$MaxInterpenetration <- log(ParsiDF$MaxInterpenetration)

ParsiDF$AverageInterpenetration <- log(ParsiDF$AverageInterpenetration)

shapiro_test(ParsiDF$MaxInterpenetration)
shapiro_test(ParsiDF$AverageInterpenetration)
ggqqplot(ParsiDF$MaxInterpenetration)
ggqqplot(ParsiDF$AverageInterpenetration)

#Let's check the assumption for each interpenetration feedback and shade condition
ParsiDF %>%
  group_by(InterpenetrationFeedback, Part) %>%
  shapiro_test(MaxInterpenetration) 

ParsiDF %>%
  group_by(InterpenetrationFeedback, Part) %>%
  shapiro_test(AverageInterpenetration) 

hist(ParsiDF$MaxInterpenetration)
hist(ParsiDF$AverageInterpenetration)

```

Good to go!


```{r}

p1 <- ggstatsplot::ggbetweenstats(
  data = ParsiDF,
  x = "InterpenetrationFeedback", #Indepedent Variable
  y = "MaxInterpenetration", # Depedent Variable
  grouping.var = "Part", # 2nd IV 
  type = "p", # parametric test i.e., p values
  pairwise.comparisons = TRUE, #compute pairwise comparisons
  pairwise.display = "significant", # show only the significant ones
  p.adjust.method = "bonferroni", # correction of p-value
  effsize.type = "unbiased", # Calculates the Hedge's g for t tests and the partial Omega for ANOVA
  xlab = "Type of Feedback", #label of X axis
  ylab = "Maximum Interpenetration", #label of y axis
  var.equal = TRUE, #Assuming Equal variances
  mean.ci = TRUE, #display the confidence interval of the mean
  notch = TRUE, #Compare the medians i.e., IQR with 95% confidence interval
  paired = TRUE #indicating that we have a within subject design
  ) 

p2 <- ggstatsplot::ggbetweenstats(
  data = ParsiDF,
  x = "InterpenetrationFeedback",
  y = "AverageInterpenetration",
  grouping.var = "Part",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
)


# Replicating the above but this time we look on the effect of the type of feedback on the DVs when the shaded is true and when it is false.
p3 <- ggstatsplot::grouped_ggbetweenstats(
  data = ParsiDF,
  x = "InterpenetrationFeedback",
  y = "MaxInterpenetration",
  grouping.var = "Part",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p4 <- ggstatsplot::grouped_ggbetweenstats(
  data = ParsiDF,
  x = "InterpenetrationFeedback",
  y = "AverageInterpenetration",
  grouping.var = "Part",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Type of Feedback",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 

# Lets check the effect of shaded condition on DVs
p5 <- ggstatsplot:: ggbetweenstats(
  data = ParsiDF,
  x = "Part",
  y = "MaxInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p6 <- ggstatsplot::ggbetweenstats(
  data = ParsiDF,
  x = "Part",
  y = "AverageInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 

p7 <- ggstatsplot::grouped_ggbetweenstats(
  data = ParsiDF,
  x = "Part",
  y = "MaxInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Maximum Interpenetration",
  sub.text = "Explicit Visual Representation" ,
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
  ) 

p8 <- ggstatsplot::grouped_ggbetweenstats(
  data = ParsiDF,
  x = "Part",
  y = "AverageInterpenetration",
  grouping.var = "InterpenetrationFeedback",
  type = "p",
  pairwise.comparisons = TRUE,
  pairwise.display = "significant",
  p.adjust.method = "bonferroni",
  effsize.type = "unbiased",
  xlab = "Target's Visual Representation",
  ylab = "Average Interpenetration",
  var.equal = TRUE,
  mean.ci = TRUE,
  notch = TRUE,
  paired = TRUE
) 
p1

p2

p3 

p4

p5 

p6

p7

p8

plist <- list(p1,p2)
plist2 <- list(p3,p4)
plist3 <- list(p5,p6)
plist4 <- list(p7,p8)

combine_plots(
  plotlist = plist, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist2, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist3, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")

combine_plots(
  plotlist = plist4, 
  title.text = "Interpenetration Box-Violin Plots",
  caption.text = "Note: Interpenetration distance is displayed in cm.",
  title.color = "black",
  caption.color = "black")



```

From the plots above we can see that #

1) there is not a significant difference between visual & electrotactile (plots 1-4).
2) the electrotactile becomes significant different from No Feedback in the 2nd part for both DVs (plots 3 & 4)
3) there in not a significant difference between electrotactile and both when we control for the parts of the experiment (plots 3 & 4) 
3) the 2nd part is significant better than 1st part (Moderate Effect) (plots 5 & 6)
4) The type of interpenetration feedback has a large effect (based on Omega squared) on the DVs (plots 1-4),
especially on the 2nd part of the experiment (plots 3 & 4)


Hedge's G Interpretation:
Small effect (cannot be discerned by the naked eye) = 0.2
Medium Effect = 0.5
Large Effect (can be seen by the naked eye) = 0.8

Reference for interpreting Omega Squared
Small effect: ω2 = 0.01;
Medium effect: ω2 = 0.06;
Large effect: ω2 = 0.14.


Let's check the Two Way Repeated Measures ANOVA
```{r Anova, echo=FALSE}
aMax <- aov_ez("ID", "MaxInterpenetration", ParsiDF,
             within = c("Part", "InterpenetrationFeedback"),
             anova_table = list(es = "pes"))

knitr::kable(nice(aMax$anova_table))
```

```{r Anova, echo=FALSE}
aAv <- aov_ez("ID", "AverageInterpenetration", ParsiDF,
             within = c("Part", "InterpenetrationFeedback"),
             anova_table = list(es = "pes"))

knitr::kable(nice(aAv$anova_table))
```

```{r}

effectsize::omega_squared(aMax, partial = TRUE, ci = 0.95)

effectsize::omega_squared(aAv, partial = TRUE, ci = 0.95)

```


We can see that every type of feedback as well as the interrelationship with the part of the experiment have a large effect on DVs!!!!!! 

Reference for interpreting Omega Squared
Small effect: ω2 = 0.01;
Medium effect: ω2 = 0.06;
Large effect: ω2 = 0.14.


Let's check the post hoc tests (Whole experiment)
```{r}

ParsiMax <- pairwise.t.test(ParsiDF$MaxInterpenetration, ParsiDF$InterpenetrationFeedback, p.adjust.method = "bonferroni",
        paired = FALSE, alternative = "two.sided")

ParsiAv <- pairwise.t.test(ParsiDF$AverageInterpenetration, ParsiDF$InterpenetrationFeedback, p.adjust.method = "bonferroni",
        paired = FALSE, alternative = "two.sided")

ParsiMax

ParsiAv
```
For both DVs, we can see that there are significant differences between

Both and NoFeedback

Visual and NoFeedback

Electrotactile and NoFeedback

Both and Electrotactile



Let's repeat the comparisons for each part of the experiment now.

Preparation of data for multiple comparisons (In Part1, Part2), 
t tests, and effect sizes based on Hedge's g (the best one for small sample sizes like this one)
```{r}
# Divide the data
Data_1st <- subset(ParsiDF, Part = "1st Part", select = c(ID, InterpenetrationFeedback, MaxInterpenetration, AverageInterpenetration))
Data_2nd <- subset(ParsiDF, Part = "2nd Part", select = c(ID, InterpenetrationFeedback, MaxInterpenetration, AverageInterpenetration))

#Covert the logs back to normal numbers, because we dont care here for the normal distribution

Data_1st$MaxInterpenetration <- exp(Data_1st$MaxInterpenetration)
Data_1st$AverageInterpenetration <- exp(Data_1st$AverageInterpenetration)

Data_2nd$MaxInterpenetration <- exp(Data_2nd$MaxInterpenetration)
Data_2nd$AverageInterpenetration <- exp(Data_2nd$AverageInterpenetration)
##### Divide Further the data per interpenetration feedback

B1 <- filter(Data_1st, InterpenetrationFeedback == "Both")

El1 <-filter(Data_1st, InterpenetrationFeedback == "Electrotactile")

No1 <- filter(Data_1st, InterpenetrationFeedback == "NoFeedback")

V1 <- filter(Data_1st, InterpenetrationFeedback == "Visual")

B2 <- filter(Data_2nd, InterpenetrationFeedback == "Both")

El2 <-filter(Data_2nd, InterpenetrationFeedback == "Electrotactile")

No2 <- filter(Data_2nd, InterpenetrationFeedback == "NoFeedback")

V2 <- filter(Data_2nd, InterpenetrationFeedback == "Visual")


#Merge them back together to create two versions (part 1 = .x, part 2 = .y) for each DV.
Rm1 <- merge(B1,B2, by = c("ID", "InterpenetrationFeedback"))
Rm2 <- merge(El1,El2, by = c("ID", "InterpenetrationFeedback"))
Rm3 <- merge(No1, No2, by = c("ID", "InterpenetrationFeedback"))
Rm4 <- merge(V1,V2, by = c("ID", "InterpenetrationFeedback"))

```


Here we will compare the types of feedback but in each part of the experiment individually
```{r}

ParsiMax1 <- pairwise.t.test(Data_1st$MaxInterpenetration, Data_1st$InterpenetrationFeedback, p.adjust.method = "bonferroni",
        paired = FALSE, alternative = "two.sided")

ParsiAv1 <- pairwise.t.test(Data_1st$AverageInterpenetration, Data_1st$InterpenetrationFeedback, p.adjust.method = "bonferroni",
        paired = FALSE, alternative = "two.sided")

ParsiMax2 <- pairwise.t.test(Data_2nd$MaxInterpenetration, Data_2nd$InterpenetrationFeedback, p.adjust.method = "bonferroni",
        paired = FALSE, alternative = "two.sided")

ParsiAv2 <- pairwise.t.test(Data_2nd$AverageInterpenetration, Data_2nd$InterpenetrationFeedback, p.adjust.method = "bonferroni",
        paired = FALSE, alternative = "two.sided")

ParsiMax1

ParsiAv1

ParsiMax2

ParsiAv2
```

For the 1st part of the experiment, we can see that there significant differences between: 
Both and NoFeedback
Visual and NoFeedback
Both and Electrotactile

For the 2nd part of the experiment, we can see that there significant differences between:
Both and NoFeedback
Visual and NoFeedback
Electrotactile and NoFeedback!!! 
Both and Electrotactile



We will run now t-tests comparing Part1 performance against Part2 performance for each Feedback type individually.
```{r}
#No we run the t-tests 
t.test(Data_1st$MaxInterpenetration,Data_2nd$MaxInterpenetration , paired=TRUE, alternative = "greater")#Part1 vs Part2

t.test(Data_1st$AverageInterpenetration,Data_2nd$AverageInterpenetration , paired=TRUE, alternative = "greater")#Part1 vs Part2


t.test(Rm1$MaxInterpenetration.x, Rm1$MaxInterpenetration.y , paired=TRUE, alternative = "greater")#Both

t.test(Rm2$MaxInterpenetration.x, Rm2$MaxInterpenetration.y , paired=TRUE, alternative = "greater")#Electrotactile

t.test(Rm3$MaxInterpenetration.x, Rm3$MaxInterpenetration.y , paired=TRUE, alternative = "greater")#NoFeedback

t.test(Rm4$MaxInterpenetration.x, Rm4$MaxInterpenetration.y , paired=TRUE, alternative = "greater")#Visual


t.test(Rm1$AverageInterpenetration.x, Rm1$AverageInterpenetration.y , paired=TRUE, alternative = "greater")#Both

t.test(Rm2$AverageInterpenetration.x, Rm2$AverageInterpenetration.y , paired=TRUE, alternative = "greater")#Electrotactile

t.test(Rm3$AverageInterpenetration.x, Rm3$AverageInterpenetration.y , paired=TRUE, alternative = "greater")#NoFeedback

t.test(Rm4$AverageInterpenetration.x, Rm4$AverageInterpenetration.y , paired=TRUE, alternative = "greater")#Visual

# All Significant


#Let's calculate now the effect size for each comparison

#first we need to prepare the data for the Hedges function

B <- filter(ParsiDF, InterpenetrationFeedback == "Both")

El <-filter(ParsiDF, InterpenetrationFeedback == "Electrotactile")

No <- filter(ParsiDF, InterpenetrationFeedback == "NoFeedback")

V <- filter(ParsiDF, InterpenetrationFeedback == "Visual")


effectsize::hedges_g("MaxInterpenetration", "Part", data = ParsiDF, correction = TRUE, paired = TRUE,) #Part of the experiment
effectsize::hedges_g("MaxInterpenetration", "Part", data = B, correction = TRUE, paired = TRUE,) #Both 
effectsize::hedges_g("MaxInterpenetration", "Part", data = El, correction = TRUE, paired = TRUE,) #Elect
effectsize::hedges_g("MaxInterpenetration", "Part", data = No, correction = TRUE, paired = TRUE,) #NoFeedback
effectsize::hedges_g("MaxInterpenetration", "Part", data = V, correction = TRUE, paired = TRUE,) #Visual

# OK the effect of Both & Electrotactile is far greater than the effect of Visual and NoFeedback

```

All comparisons (Interpenetration Feedback per part of the experiment) were significant!!! 
However, the both and the electrotactile have a large effect!!!, 
while the No Feedback has a moderate to small size of effect
and the Visual has a moderate effect.

Also, the part of the experiment has a moderate to large size effect.

Hedge's G Interpretation:
Small effect (cannot be discerned by the naked eye) = 0.2
Medium Effect = 0.5
Large Effect (can be seen by the naked eye) = 0.8

